---
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Course Schedule

| CBW’s Introduction to R workshop (INR) 2024 |                                                     |            |                                                       |   |
|:-------------------------------------------:|:---------------------------------------------------:|:----------:|:-----------------------------------------------------:|---|
|                    Day 1                    |                                                     |    Day 2   |                                                       |   |
|                   June 11                   |                                                     |   June 12  |                                                       |   |
|                  Time (EDT)                 |                        Module                       | Time (EDT) |                         Module                        |   |
|                     8:30                    |                 Arrivals & Check-in                 |    8:30    |                        Arrivals                       |   |
|                     9:00                    |                 Welcome (Nia Hughes)                |    9:00    | Review & Module 3: Loops and functions (Frances Wong) |   |
|                     9:30                    |      Module 1: Getting to Know R (Frances Wong)     |    10:00   |                     Break (15min)                     |   |
|                    10:30                    |                    Break (15min)                    |    10:15   |         Module 3: Loops and functions (cont'd)        |   |
|                    10:45                    |         Module 1: Getting to Know R (cont'd)        |    11:00   |                     Break (15min)                     |   |
|                    11:15                    |                    Break (15min)                    |    11:15   |         Module 3: Loops and functions (cont'd)        |   |
|                    11:30                    |         Module 1: Getting to Know R (cont'd)        |    12:00   |                Class Photo + Break (1h)               |   |
|                    12:00                    |                      Break (1h)                     |    13:00   |       Module 4: Linear regression (Frances Wong)      |   |
|                    13:00                    | Module 2: Exploring your data in R   (Frances Wong) |    14:00   |                     Break (15min)                     |   |
|                    14:00                    |                    Break (15min)                    |    14:15   |          Module 4: Linear regression (cont'd)         |   |
|                    14:15                    |    Module 2: Exploring your data in R   (cont'd)    |    15:15   |                     Break (15min)                     |   |
|                    15:15                    |                    Break (15min)                    |    15:30   |                     Short Project                     |   |
|                    15:30                    |               Review and Short project              |    17:00   |                Survey & Closing Remarks               |   |
|                    17:30                    |                       Finished                      |    17:30   |                        Finished                       |   |

+++

```{r}
#install.packages("tidyverse")

library(tidyverse)
```

# ToastUI Schedule ?

```{r}
library(toastui)
library(tidyverse)
```

```{r, echo=FALSE}
calendar(cal_demo_data("week"), view = "week", height = 1000) %>%
cal_week_options(
  startDayOfWeek = 1,
  workweek = TRUE
) %>% 
cal_props(cal_demo_props())

# defaultDate = "2024-06-11"
# height - sorta hardcoding it so that it looks nice on a regular screen size

# detail popup has edit/delete buttons, but also gives a description, but we probably don't want to have edit and delete buttons, but nice to have a description (to remove, add useDetailPopup = FALSE, TRUE is default)
```

```{r, echo=FALSE}
library(toastui)
cal_demo_data()
cal_demo_data("week")
```
```{r, echo=FALSE}
library(toastui)

Data_Frame <- data.frame (
  calendarID = c(1, 2, 3, 2),
  title = c("A", "B", "C", "D"),
  body = c("aaaaa", "bbbb", "cccccc", "dddddd"),
  start = c("2024-10-14 8:00:00", "2024-10-14 14:00:00", "2024-10-16 08:00:00", "2024-10-17 08:00:00"),
  end = c("2024-10-14 12:00:00", "2024-10-14 18:00:00", "2024-10-16 11:00:00", "2024-10-17 19:00:00"),
  category = c("time", "time", "time", "time")
)

calendar(Data_Frame, view = "week", height = 1000, defaultDate = "2024-10-18") %>% 
cal_week_options(
  startDayOfWeek = 1,
  workweek = TRUE
) %>% 
cal_props(cal_demo_props()) 
```
```{r}
library(toastui)
library(readxl)

my_data <- read_excel("datasets/sample_toastui_excel.xlsx", sheet = "Sheet1")

calendar(my_data, view = "week", height = 1000, defaultDate = "2024-10-18") %>% 
cal_week_options(
  startDayOfWeek = 1,
  workweek = TRUE
) %>% 
cal_props(cal_demo_props()) 
```
